### 2025-02-12 short/sections/selected-papers.tex
Update selected-papers.tex

\begin{benumerate}{10}

\item{González-Bustamante, B. (2025). Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets. {\itshape Social Science Computer Review}. \\ DOI :\href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}. \faBriefcase\ $\,$ {\bfseries Writing sample}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}

@@

%% \item{González-Bustamante, B. (2019). Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay. {\itshape Convergencia. Revista de Ciencias Sociales}, 80, 1--27. {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}. {\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}

@@

%% \pagebreak

>>>>

\begin{benumerate}{11}

\item{González-Bustamante, B. (2025). Machine Learning and Political Events: Application of a Semi-Supervised Approach to Produce a Dataset on Presidential Cabinets. {\itshape Social Science Computer Review}. \faBriefcase\ {\bfseries Writing sample}. DOI: \href{https://doi.org/10.1177/08944393251315917}{\textcolor{blue}{10.1177/08944393251315917}}.}\vspace{1mm} %% \\ \faBriefcase\ {\bfseries Job market paper}.}\vspace{1mm}

@@

\item{González-Bustamante, B. (2019). Brechas, representación y congruencia élite-ciudadanía en Chile y Uruguay. {\itshape Convergencia. Revista de Ciencias Sociales}, 80, 1--27. {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{\textcolor{blue}{10.29101/crcs.v26i80.11097}}. {\scshape \footnotesize SocArXiv:} \\ \href{https://doi.org/10.31235/osf.io/cqym8}{\textcolor{blue}{10.31235/osf.io/cqym8}}.}\vspace{1mm} %% {\scshape url:} \href{https://www.redalyc.org/jatsRepo/105/10559568002/index.html}{\textcolor{blue}{www.redalyc.org}}

@@

 \pagebreak
